### 2023-06-23 manuscript.tex
now better description (if a bit long!) [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/98a96b025d3d28782653c0302c3b390cab049c0c.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/98a96b025d3d28782653c0302c3b390cab049c0c/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5357449612

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/196b2c0a09b766bbcc026f7504f34a805280a9fc/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/196b2c0a09b766bbcc026f7504f34a805280a9fc}{stain/2022-fdo-paper@196b2c0}
on June 23, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/98a96b025d3d28782653c0302c3b390cab049c0c/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/98a96b025d3d28782653c0302c3b390cab049c0c}{stain/2022-fdo-paper@98a96b0}
on June 23, 2023.
